% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX
% ----------------------------------------------------------------------
% Daniel R. Driver
% Curriculum vitae
%
% LaTeX template derived from: http://nitens.org/taraborelli/cvtex
% ----------------------------------------------------------------------

\documentclass[11pt]{article}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{letterpaper,
          textwidth=5.5in,
          textheight=8.5in,
          marginparsep=7pt,
          marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage{fontspec,realscripts}
\defaultfontfeatures{Mapping=tex-text,Numbers=OldStyle}
\setromanfont{Arno Pro}
\setsansfont{Scala Sans Pro}
\setmonofont[Scale=MatchLowercase]{Menlo}
\frenchspacing
\usepackage[usenames,dvipsnames]{color}

%\renewcommand\tiny{\fontsize{6}{9}\selectfont}
%\renewcommand\scriptsize{\fontsize{7}{10}\selectfont}
%\renewcommand\footnotesize{\fontsize{8}{11}\selectfont}
%\renewcommand\small{\fontsize{9}{11}\selectfont}
%\renewcommand\normalsize{\fontsize{10}{12}\selectfont}% 10pt base size
%\renewcommand\large{\fontsize{12}{14}\selectfont}
%\renewcommand\Large{\fontsize{14}{16}\selectfont}
%\renewcommand\LARGE{\fontsize{16}{18}\selectfont}
%\renewcommand\huge{\fontsize{19}{17}\selectfont}
%\renewcommand\Huge{\fontsize{22}{24}\selectfont}

% ---- CUSTOM COMMANDS
\newcommand{\amper}{\emph{\&}}
\newcommand{\html}[1]{\href{#1}{\footnotesize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\footnotesize\textsc{[pdf]}}}
\newcommand{\audio}[1]{\href{#1}{\footnotesize\textsc{[audio mp3]}}}
\newcommand{\doi}[1]{\href{https://doi.org/#1}{\footnotesize\textsc{[doi]}}}
\newcommand{\smallprint}[1]{\fontspec{{Arno Pro}\fontsize{10pt}{13pt}\color{Gray}\selectfont #1}}%
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\footnotesize #1}}
\renewcommand*{\raggedrightmarginnote}{}
\setlength{\marginparsep}{14pt}
\reversemarginpar

% QUOTING FOR DETAILS
\usepackage[font=footnotesize,leftmargin=0em,vskip=0em]{quoting}

% EURO DATE
\makeatletter
\def\today{\number\day\space\ifcase\month\or% revised following Flynn 2.13
  January\or February\or March\or April\or May\or June\or
  July\or August\or September\or October\or November\or December\fi
  \space\number\year}
\makeatother

% CUSTOM TITLES
\usepackage{titlesec}
\titleformat*{\section}{\Large\normalfont}
\titleformat*{\subsection}{\normalsize\normalfont\scshape}
\titleformat*{\subsubsection}{\normalsize\normalfont}
\titleformat*{\paragraph}{\normalsize\normalfont}
\titleformat*{\subparagraph}{\normalsize\normalfont}
\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\textsf{#1}}

% PDF SETUP
\usepackage[bookmarks, colorlinks, breaklinks,
	pdftitle={Daniel R. Driver - curriculum vitae},
	pdfauthor={Daniel R. Driver},
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\Huge Daniel R. Driver}\\[3em]
%
Atlantic School of Theology\\
660 Francklyn Street\\
Halifax, Nova Scotia\\
\textsc{b3h 3b5} • Canada\\[1em]

%
Office: Library N-5; Phone: 902-425-7051\\
Email: \href{mailto:ddriver@astheology.ns.ca}{ddriver@astheology.ns.ca}\\[1em]
%
Born: 1979 in Portland, Oregon\\
Nationality: American; Permanent Resident of Canada
\vfill

% ----------------------------------------------------------------------
\section*{Academic positions}
% ----------------------------------------------------------------------
\years{2020} \emph{Acting Dean} of Atlantic School of Theology
	\begin{quoting}
	From July to December this year I am standing in to serve as AST's chief academic officer.
	\end{quoting}

\years{2016---} \emph{Associate Professor} of Hebrew Bible/Old Testament, Atlantic School of Theology
	\begin{quoting}
	In addition to covering the basics for graduate-level survey and
	language requirements, here I offer a representative rotation of
	courses from the Tanakh by covering selections from the Law, the
	Prophets, and the Writings.
	\end{quoting}

%\years{2015--2016} \emph{Associate Professor} of Old Testament, Tyndale University College

\years{2008--2016} \emph{Assistant} and (from 2015) \emph{Associate Professor} of Old Testament, Tyndale University College
	\begin{quoting}
	Here I taught a regular survey of the HB/OT, four semesters of
	biblical Hebrew, and an array of upper-division courses.
%	upper-division courses on:
%	the Pentateuch,
%	Genesis,
%	Creation,
%	the Decalogue,
%	Leviticus,
%	the Book of the Twelve,
%	Psalms,
%	Ecclesiastes,
%	Canon and the Rule of Faith,
%	the Historical Geography of Israel,
%	the Old Testament as Christian Scripture,
%	the Fate of the Dead,
%	and Forgiveness.
	\end{quoting}

\years{2011--2013}
\emph{Associate Dean} of the University College, Tyndale University College and Seminary
	\begin{quoting}
	In this role I coordinated a self-study required by the Ontario
	Ministry of Training, Colleges, and Universities.
	\end{quoting}

% ----------------------------------------------------------------------
%\section*{Areas of specialized interest}
% ----------------------------------------------------------------------
%--- Late 20\textsuperscript{th} century Old Testament and Biblical Theology\\
%--- Canonical approaches to Christian scripture\\
%--- Biblical reception history (\emph{Wirkungsgeschichte})\\
%--- Genesis, and biblical worlds for time\\
%--- The Psalms\\
%--- Death and dying in the Hebrew Bible/Old Testament

% ----------------------------------------------------------------------
\section*{Education}
% ----------------------------------------------------------------------

\years{2005--2008}
\textsc{PhD} in Divinity, University of St Andrews, Scotland
	\begin{quoting}
	Title: ``Brevard Childs: The Logic of Scripture's Textual Authority in the Mystery of Christ.'' \pdf{http://hdl.handle.net/10023/754}\\
	Examination: 3 October 2008, by Grant Macaskill (internal) and R.W.L. Moberly (external). Typographical revisions.
	\end{quoting}

\years{2004--2005}
\textsc{MPhil} coursework, University of St Andrews, Scotland (upgraded to \textsc{PhD} track after one year)
	\begin{quoting}
	Completed with Honours. Modules: Advanced Biblical Exegesis, Great Theological Texts, The Dead Sea Scrolls.
	\end{quoting}

\years{1998--2002}
\textsc{BA} in English Literature, Wheaton College, Illinois (\emph{magna cum laude})

% ----------------------------------------------------------------------
\section*{Awards}
% ----------------------------------------------------------------------

\years{2019}
Leni Groeneveld Grant for Research Assistance in 2019–2020, Pine Hill Divinity Hall, Halifax

\years{2019}
Invited Participant, Dabar Conference on Divine Action, Contingency, and Modern Science (Chicago)% 12-15 June 2019 (by-invitation); From website: The Dabar Conference is a by-invitation event gathering 60+ evangelicals together from different disciplines, denominations, and institutions with the goal of orienting evangelical theologians to the relevant recent work in the natural sciences and to promoting scholarship in the field of the doctrine of creation.

\years{2018}
Nominated Participant, Luce Sponsored Workshop on Interreligious Pedagogies (Denver)% 16 November 2018 w/ Judith Berling

\years{2018}
Nominated Participant, ATS Roundtable Seminar for Midcareer Faculty (Orlando) % 6–8 April 2018

\years{2017}
Leni Groeneveld Grant for Research Assistance in 2017–2018, Pine Hill Divinity Hall, Halifax

\years{2007}
Fondation Catholique Ecossaise Scholarship for a summer term at L'Institut Catholique de Paris

%\years{2002}
%Honorable Mentions in the J. G. Jameson Critical Essay Contest and the Lowell Grabill Poetry Contest

% ----------------------------------------------------------------------
\section*{Publications \amper{} papers}
% ----------------------------------------------------------------------

\subsection*{books}
% ----------------------------------------------------------------------

\years{2022}
\emph{Creation}. Co-authoring with Sean McDonough. Forthcoming in the
Topics of Biblical Theology (TOBITH) series, ed. Reinhard Feldmeier and
Hermann Spieckermann. Tübingen: Mohr Siebeck, 2022. Under contract.

\years{2010, 2012}
\emph{Brevard Childs, Biblical Theologian: For the Church’s One Bible}.
Forschungen zum Alten Testament II/46. Tübingen: Mohr Siebeck, 2010. A
thorough rewriting of my doctoral thesis, this monograph makes my study
of Childs more comprehensive. The first edition was then corrected and
expanded for a North American edition (Grand Rapids: Baker Academic,
2012). 150,000 words.
\html{http://danieldriver.com/bsc/}

\subsection*{edited volumes}
% ----------------------------------------------------------------------

\years{2021}
\emph{Canon as Rule and Guide: The Collected Essays of Brevard S. Childs}.
Forschungen zum Alten Testament I. Tübingen: Mohr Siebeck, 2020. In preparation.

\years{2009}
\emph{The Epistle to the Hebrews and Christian Theology}. Edited with
Richard Bauckham, Trevor Hart and Nathan MacDonald. Grand Rapids:
Eerdmans, 2009. 140,000 words.

\years{2008}
\emph{A Cloud of Witnesses: The Theology of Hebrews in Its Ancient
Contexts}. Edited with Richard Bauckham, Trevor Hart and Nathan
MacDonald. Library of New Testament Studies (JSNTS) 387. London: T\&T
Clark, 2008. 100,000 words.

\subsection*{articles \amper{} translations}
% ----------------------------------------------------------------------

\years{2021}
``Sabbath and Land.'' Forthcoming in \emph{T\&T Clark Companion to the
Doctrine of Creation}. Edited by Jason Goroncy. London: T\&T Clark,
2021. 6,000 words. Under contract.

\years{2020}
``God in Scriptural Proximity: Notes on the Contribution of Christopher
Seitz.'' Forthcoming in \emph{The Identity of Israel’s God in Christian
Scripture}. Edited by Donald Collett, Mark Elliott, Mark Gignilliat, and
Ephraim Radner. Atlanta: SBL, 2020. Commissioned by the editors. 6,500
words. In press.

\years{2020}
``On Difficulty and Psalm 2.'' Forthcoming in \emph{The Identity of
Israel’s God in Christian Scripture}. Edited by Donald Collett, Mark
Elliott, Mark Gignilliat, and Ephraim Radner. Atlanta: SBL, 2020.
Commissioned by the editors. 8,500 words. In press.

\years{2019}
``Genesis by the Numbers: A Reassessment of the Years of the Patriarchs,
Beginning with the Joseph Story.'' \emph{Journal of the Bible and its
Reception} 6.1 (May 2019): 67–95. 11,000 words.
\doi{10.1515/jbr-2019-1003}

\years{2019}
``Currents in Old Testament: Interpreting Psalms and the Psalter.''
\emph{Didaktikos: Journal of Theological Education} 2.5 (April 2019):
45–46. Commissioned by the editors. 1,000 words.

\years{2015}
``Forgiveness.'' Pages 371--377 in \emph{The Oxford Encyclopedia of the
Bible and Theology}. Edited by Samuel E. Balentine et al. Oxford: Oxford
University Press, 2015. 4,000 words.

\years{2013}
``Childs and the Canon or Rule of Faith.'' Pages 243--278 in \emph{The
Bible as Christian Scripture: The Work of Brevard S. Childs}. Edited by
Christopher Seitz and Kent Richards. Atlanta: SBL, 2013. 14,000 words.
\pdf{http://danieldriver.com/assets/pdf/publications/Driver_2013.pdf}

\years{2013}
Translation of Bernd Janowski, ``The Contrastive Unity of Scripture: On
the Hermeneutics of the Biblical Canon.'' Pages 37--62 in \emph{The
Bible as Christian Scripture: The Work of Brevard S. Childs}. Edited by
Christopher Seitz and Kent Richards. Atlanta: SBL, 2013. 10,000 words.
\\\\% force break

\years{2012}%
``Canonical Criticism HB/OT.'' With Nathan MacDonald. Pages 924–926 in
\emph{The Encyclopedia of the Bible and its Reception}, Vol. 4. Edited
by Hermann Spieckermann et al. 30 vols. Berlin/New York: Walter de
Gruyter, 2012.

\years{2012}
``Childs, Brevard S.'' With Nathan MacDonald. Pages 126–127 in \emph{The
Encyclopedia of the Bible and its Reception}, Vol. 4. Edited by Hermann
Spieckermann et al. 30 vols. Berlin/New York: Walter de Gruyter, 2012.

\years{2008}
``Later Childs.'' \emph{Princeton Theological Review} 38 (Spring 2008):
117--129.
%\pdf{http://www.princetontheologicalreview.org/issues_pdf/38.pdf}

%\\ % force break - if necessary

\subsection*{select reviews}
% ----------------------------------------------------------------------

\years{2020}
Review of Stephen O. Presley, \emph{The Intertextual Reception of
Genesis 1–3 in Irenaeus of Lyons}. \emph{Pro Ecclesia} 29/2 (2020):
244--247.
\doi{10.1177/1063851220907982}

\years{2015}
Review of Charles E. Shepherd, \emph{Theological Interpretation and
Isaiah 53: A Critical Comparison of Bernhard Duhm, Brevard Childs, and
Alec Motyer}. \emph{Journal of Theological Studies} 66/2 (2015):
722--724.
\doi{10.1093/jts/flv103}

\years{2012}
Review of Denis Minns, \emph{Irenaeus: An Introduction}. \emph{Toronto
Journal of Theology} 28/2 (2012): 322--323.
\doi{10.1353/tjt.2012.0054}

%\years{2011}
%Review of Michael Legaspi, \emph{The Death of Scripture and the Rise of
%Biblical Studies} (Oxford Studies in Historical Theology).
%\emph{Lente.net: Bulletin of Scripture and Theology} (2008).
%\html{http://www.lente.net/2013/11/legaspi/}

\years{2008}
Review of Georg Steins and Egbert Ballhorn, eds., \emph{Der Bibelkanon
in der Bibelauslegung: Beispielexegesen und Methodenreflexionen}.
\emph{Review of Biblical Literature} [bookreviews.org] (2008).
\pdf{http://bookreviews.org/pdf/6401_6893.pdf}

\subsection*{select papers \amper{} presentations}
% ----------------------------------------------------------------------

\years{May 2020}
``The Sense of a Beginning: Three Ways to Read the Bible’s First
Sentence.'' Webinar Series: Talks with Faculty \& Friends of Atlantic
School of Theology. Halifax, 15 May 2020.

\years{Mar 2019}
``Ecclesiastes in Lent.'' Parish retreat talk, St Paul's Anglican
Church. Halifax, 9 March 2019.

\years{Oct 2017}
``Counting Time in the Joseph Story: Toward a New Appreciation of the
Ages of the Patriarchs.'' Paper presented to AST/SMU Faculty Symposium,
St Mary's University. Halifax, 20 October 2017.

\years{Feb 2017}
``Creation for Christians.'' Parish retreat talks, St Paul's Anglican
Church. Halifax, 11 February 2017.

\years{May 2017}
A Short Introduction to the Old Testament. Four lectures given at the
Moosonee School of Ministry, training Anglican lay leaders among the
James Bay Cree. Cochrane, ON, 25–28 May 2017.

\years{Jan 2016}
``What's Wrong with Steinmetz’s `Superiority of Pre-Critical
Exegesis.'\,'' Paper presented at the Annual Faculty-Student Forum,
Tyndale University College. Toronto, 13 January 2016.

\years{May 2014}
``Of Time and Ecclesiastes." Paper presented at the Wycliffe Centre for
Scripture and Theology, Wycliffe College, University of Toronto.
Toronto, 9 May 2014.

\years{July 2013}
``From Lord God to Father God, but Why Not Christ the Lord?" Invited
paper for a review panel on R.~Feldmeier and H. Spieckermann's \emph{Der
Gott der Lebendigen / God of the Living}, with responses by the authors,
presented at International SBL 2013. St. Andrews, 10 July 2013.

\years{Nov 2011}
``Psalm 2 in Antiochene Exegesis: On the Difficulty of Identifying
Nations and Peoples." Paper presented at SBL 2011. San Francisco, 17
November 2011.
\audio{http://danieldriver.com/assets/mp3/2012-02-04_Symposium_Daniel_Driver.mp3} % Audio from when the paper was re-read in Toronto, 4 February 2012.
%\audio{http://www.tyndale.ca/sites/default/files/2012-02-04_Symposium_Daniel_Driver.mp3}

\years{May 2011}
``Assessing the Brazos Theological Commentary Series: R.\,R. Reno's
Genesis Commentary." Paper presented at the Wycliffe Centre for
Scripture and Theology. Toronto, 13 May 2011.

\years{Sept 2010}
``In your light do we see light,'' ``The unfolding of your words gives
light,'' and ``I said, `I will be wise,' but it was far from me.'' Three
papers presented to the faculty of Wycliffe College. Toronto, 2 September 2010.

\years{Aug 2009}
``Canon as \emph{Regula Fidei}: On B. Childs' Renewal of Canon along
Dogmatic Lines.'' Paper presented at EABS 2009. Lincoln, England, 28
August 2009.
%\\% force break

\years{July 2009}
``Reckoning Time in Ussher and Bede: The End and Beginning of Biblical
Chronology in the British Isles.'' Paper presented at the St Andrews
Conference on Genesis and Christian Theology. St Andrews, 15 July 2009.

\years{Nov 2007}
``For a Generation to Come: The Scope of Psalm 102 in Reception and
Recent Research.'' Paper presented at SBL 2007. San Diego, 17 November
2007.

%\years{Oct 2007}
%``Brevard Childs and His Followers.'' Paper presented at the Scripture
%\& Theology Seminar, St Mary’s College. St Andrews, 24 October 2007.

%\years{Mar 2007}
%``Response to Ross Wagner, `Greek Isaiah and the Septuagint as Christian
%Scripture.'\,'' Response presented at the Joint Biblical/Systematic
%Theology Seminar, St Mary’s College. St Andrews, 14 March 2007.

%\years{Dec 2006}
%``Midrash, \emph{Kanonbewußtsein}, and the `Mystery of Israel.'\,''
%Paper presented at the Scripture \& Theology Seminar, St Mary’s College.
%St Andrews, 6 December 2006.

%\subsection*{in preparation}
% ----------------------------------------------------------------------
%
%\years{Oct 2011}
%Review of  David Burrell, Carlo Cogliati, Janet Soskice and William R.
%Stoeger, eds., \emph{Creation and the God of Abraham}. \emph{Review of
%Biblical Literature} [bookreviews.org] (2011).

% ----------------------------------------------------------------------
\section*{Teaching experience}
% ----------------------------------------------------------------------

%\subsection*{positions held}
% ----------------------------------------------------------------------

\years{2008---}
\emph{Biblical Studies \& Theology}: Only full-time instructor in HB/OT in a small department or university
%	\begin{quoting}
%	TK
%	\end{quoting}

\years{2005}
\emph{Tutor} for Nathan MacDonald, The History and Religion of Ancient Israel, University of St Andrews
%	\begin{quoting}
%	Taught undergraduates in an introductory module, facilitating
%	seminar-style discussions and marking their essays.
%	\end{quoting}

\years{2002--2004}
\emph{Rhetoric School Teacher}, Cair Paravel-Latin School, Kansas
	\begin{quoting}
	Taught high school Classics of Western Literature,
	Creative Writing, US History, Political \& Moral Philosophy.
	\end{quoting}

\years{2001--2002}
\emph{Student Director}, Writing Center, Wheaton College, Illinois
	\begin{quoting}
	Tutored university students across the disciplines and managed
	a staff of twelve writing consultants.
	\end{quoting}

\years{2001--2002}
\emph{Teaching Assistant} to Jeffry Davis, English Literature, Wheaton College, Illinois
%	\begin{quoting}
%	Marked writing assignments, proofed a book manuscript, and
%	occasionally taught courses or chaired seminars in the professor’s
%	absence.
%	\end{quoting}

%\years{2001}
%\emph{English Language Counselor}, English Language Institute of China, Guiyang, Guizhou
%	\begin{quoting}
%	Instructed fifteen middle school students in conversational English.
%	\end{quoting}


\subsection*{postgraduate courses taught (2016---)}
% ----------------------------------------------------------------------

\years{\textsc{bf} 1001}
Hebrew Bible/Old Testament \html{http://danieldriver.com/courses/bf-1001/}

\years{\textsc{hb} 2201}
Beginning Biblical Hebrew I \html{http://danieldriver.com/courses/hb-2201/}

\years{\textsc{hb} 2202}
Beginning Biblical Hebrew II \html{http://danieldriver.com/courses/hb-2202/}

\years{\textsc{hb} 3111}
The Book of Genesis \html{http://danieldriver.com/courses/hb-3111/}

\years{\textsc{hb} 3112}
Psalms in Interpretation \html{http://danieldriver.com/courses/hb-3112/}

\years{\textsc{hb} 3113}
The Ten Commandments \html{http://danieldriver.com/courses/hb-3113/}

\years{\textsc{hb} 3114}
The Twelve Prophets \html{http://danieldriver.com/courses/hb-3114/}

\years{\textsc{hb} 3115}
Exodus and the Life of Moses \html{http://danieldriver.com/courses/hb-3115/}

\years{\textsc{hb} 3116}
Ecclesiastes \html{http://danieldriver.com/courses/hb-3116/}

\years{\textsc{hb/st} 3001}
Christian Doctrine and the Old Testament \html{http://danieldriver.com/courses/hbst-3001/}

\years{\textsc{st/hb} 3001}
The Eucharist in Ecumenical Perspective \html{http://danieldriver.com/courses/sthb-3101/}


\subsection*{undergraduate courses taught (2008--2016)}
% ----------------------------------------------------------------------

\years{\textsc{bsth} 101}
Old Testament Scripture %\html{http://danieldriver.com/}

\years{\textsc{bsth} 307}
Israel Study Tour: Historical Geography of the Bible %\html{http://danieldriver.com/notes/israel-study-tour/}

\years{\textsc{bsth} 310}
The Pentateuch

\years{\textsc{bsth} 321}%\years{\textsc{rlgs} 311}
The Ten Commandments %Text \& Interpretation: The Ten Commandments

\years{\textsc{rlgs} 314}
Text \& Interpretation: The Book of the Twelve

\years{\textsc{rlgs} 321}
Text \& Interpretation: Genesis

\years{\textsc{rlgs} 326}
Text \& Interpretation: Psalms

\years{\textsc{bsth} 440}
Topics in Biblical Theology: Creation and the Old Testament

\years{\textsc{bsth} 440}
Topics in Biblical Theology: Ecclesiastes

\years{\textsc{rlgs} 445}
Topics in Biblical Theology: The Fate of the Dead

\years{\textsc{rlgs} 446}
Topics in Biblical Theology: Canon and the Rule of Faith

\years{\textsc{rlgs} 448}
Topics in Biblical Theology: The Old Testament at Christian Scripture

\years{\textsc{rlgs} 450}
Directed Study in: Leviticus

\years{\textsc{rlgs} 497, 9}
Honours Thesis in Religious Studies I \& II

\years{\textsc{hebr} 201, 2}
Introduction to Biblical Hebrew I \& II

\years{\textsc{hebr} 301, 2}
Readings in Biblical Hebrew I \& II

% ----------------------------------------------------------------------
%\section*{Service to the profession}
\section*{Service to church \amper{} academy}
% ----------------------------------------------------------------------

\years{2020---}
\emph{Member}, Strategic Planning Committee, Atlantic School of Theology

\years{2020}
\emph{Member}, Management Advisory Committee, Atlantic School of Theology

\years{2019--2021}
\emph{Member}, Faculty Search Committee, Atlantic School of Theology

\years{2018--2019}
\emph{Member}, Interfaith Committee, Atlantic School of Theology

\years{2018---}
\emph{Parish Theologian}, St Paul's Anglican Church, Halifax, NS \html{http://www.stpaulshalifax.org}

\years{2017---}
\emph{Treasurer}, Atlantic School of Theology Faculty Association (ASTFA) \html{http://www.astfa.ca}

\years{2018--2019}
\emph{Chief Negotiator} for ASTFA, 4th Collective Agreement between AST and ASTFA

\years{2016---}
\emph{Faculty Representative}, Board of Governors, Atlantic School of Theology

\years{2016---}
\emph{Senate Delegate}, Honourary Degrees Committee, Atlantic School of Theology

\years{2014--2016}
\emph{Secretary-Treasurer}, Faculty Association, Tyndale University College

%\years{2013--2016}
%\emph{Faculty Representative}, Academic Standards Committee, Tyndale University College

%\years{2012---}
%\emph{Designer and Co-editor} of the open-access \emph{Lente.net: Bulletin of Scripture \& Theology}
%\html{http://www.lente.net}

\years{2011--2016}
\emph{Co-coordinator}, Wycliffe Centre for Scripture and Theology, University of Toronto
%\html{http://www.lente.net/category/wcst-news/}

\years{2011--2013}
\emph{Associate Dean}, Tyndale University College, Tyndale UC \& Seminary

%\years{2010--2014}
%\emph{Faculty Representative}, Campus Transitions Committee, Tyndale UC \& Seminary

\years{2009--2016}
\emph{Deputy Rector's Warden}, St Matthew’s Anglican Church in Riverdale, Toronto

\years{2009--2013}
\emph{Faculty Representative}, UC Academic Council, Tyndale UC \& Seminary

\years{2006--2007}
\emph{Student Facilitator}, Scripture \& Theology Research Seminar, University of St Andrews
	\begin{quoting}
	Assisted in a postgraduate research seminar convened by Christopher
	Seitz and Mark Elliott.
	\end{quoting}

\years{2005--2006}
\emph{Conference Administrator}, St Andrews Conference on Hebrews \& Christian Theology
	\begin{quoting}
	Administrator for a large international conference that took place
	in July 2006. Managed a budget of £35,000.
	\end{quoting}

% ----------------------------------------------------------------------
%\section*{Research projects under development}
% ----------------------------------------------------------------------

%\years{2015---} ``The Transposition of Forgiveness.''
%A project statement is available on request.
% A project statement for the Reid Trust, in Ontario, 1 April 2015.

%\years{2014---} ``Genesis in Time: Genesis \liningnums{1--11} and the Reification of Time.''
%A project statement is available on request.
% A project statement for a Fulbright grant to research in Germany, 30 July 2014.

% ----------------------------------------------------------------------
\section*{References}
% ----------------------------------------------------------------------

Dr Nathan MacDonald --- \emph{Primary supervisor of \textsc{PhD}}\\
Reader in the Interpretation of the Old Testament, University of Cambridge\\
%St John's College\\
%Cambridge \textsc{cb2 1tp}, UK\\
%Phone: (+44) 01223 763046\\
Email: \href{mailto:nm10011@cam.ac.uk}{nm10011@cam.ac.uk}\\

Professor Walter Moberly --- \emph{External examiner of \textsc{PhD}}\\
Professor of Old Testament, Durham University\\
%Department of Theology and Religion\\
%Abbey House, Palace Green\\
%Durham \textsc{dh1 3rs}, UK\\
%Phone: (+44) 1913 343953	\\
Email: \href{mailto:r.w.l.moberly@durham.ac.uk}{r.w.l.moberly@durham.ac.uk}\\

Professor Christopher Seitz --- \emph{Teacher in St Andrews, colleague in Toronto}\\
Senior Research Professor in Old Testament, University of Toronto\\
%Wycliffe College, 5 Hoskin Ave\\
%Toronto, Ontario \textsc{m5s 1h7}\\
%6303 Lakehurst Avenue\\
%Dallas, TX 75230\\
%Phone: 214-471-8934\\
Email: \href{mailto:CSeitz@wycliffe.utoronto.ca}{CSeitz@wycliffe.utoronto.ca}\\

Professor Ephraim Radner --- \emph{Colleague in Toronto}\\
Professor of Historical Theology, University of Toronto\\
%Wycliffe College, 5 Hoskin Ave\\
%Toronto, Ontario \textsc{m5s 1h7}\\
%Phone: 416-946-3533\\
Email: \href{mailto:e.radner@wycliffe.utoronto.ca}{e.radner@wycliffe.utoronto.ca}\\

%Dr Sean McDonough --- \emph{Interdisciplinary colleague and co-author}\\
%Professor of New Testament, Gordon-Conwell Theological Seminary\\
%Gordon-Conwell Theological Seminary\\
%130 Essex Street\\
%South Hamilton, MA 01982\\
%Phone: 978-468-7111 ext. 4091\\
%Email: \href{mailto:smcdonough@gordonconwell.edu}{smcdonough@gordonconwell.edu}\\

%Dr Benjamin Reynolds --- \emph{Colleague in Toronto, formerly my Department Chair}\\
%Associate Professor of New Testament, Tyndale University College\\
%Tyndale University College, 3377 Bayview Ave\\
%Toronto, Ontario \textsc{m2m 3s4}\\
%Phone: 416-226-6620 ext. 2145\\
%Email: \href{mailto:breynolds@tyndale.ca}{breynolds@tyndale.ca}\\

%Rev Dr Robert Fennell --- \emph{Dean and colleague in Halifax}\\
%Academic Dean \& Associate Professor of Historical and Systematic Theology\\
%Atlantic School of Theology, Halifax\\
%660 Francklyn Street, Halifax, Nova Scotia \textsc{b3h 3b5}\\
%Phone: 902-425-3298\\
%Email: \href{mailto:rfennell@astheology.ns.ca}{rfennell@astheology.ns.ca}

%Dr Alyda Faber --- \emph{Colleague in Halifax}\\
%Associate Professor of Systematic Theology and Ethics, Atlantic School of Theology\\
%Atlantic School of Theology, 660 Francklyn Street\\
%Halifax, Nova Scotia \textsc{b3h 3b5}\\
%Phone: 902-423-2242\\
%Email: \href{mailto:afaber@astheology.ns.ca}{afaber@astheology.ns.ca}\\

%Dr Douglas Loney --- \emph{Retired colleague, Dean of Tyndale UC when I was Associate Dean}\\
%Emeritus Dean of Tyndale UC, Professor of English Literature\\
%8 Jordan Lane, Barry's Bay, Ontario \textsc{k0j 1b0}\\
%Phone: 613-756-6117\\
%Email: \href{mailto:j.douglasloney@gmail.com}{j.douglasloney@gmail.com}\\

%Dr Marion Taylor --- \emph{external examiner on my tenure committee}\\
%Professor of Old Testament, University of Toronto\\
%Wycliffe College, 5 Hoskin Ave\\
%Toronto, Ontario \textsc{m5s 1h7}\\
%Phone: 416-946-3542\\
%Email: \href{mailto:m.taylor@utoronto.ca}{m.taylor@utoronto.ca}\\

%Rev. Ajit John --- \emph{Lawyer and bi-vocational priest in charge at my parish church, St. Matthew's Riverdale}\\
%The Law Society of Upper Canada\\
%Osgoode Hall, 130 Queen Street West\\
%Toronto, Ontario \textsc{m5h 2n6}\\
%Phone: 416-947-3922\\
%Email: \href{mailto:ajohn@lsuc.on.ca}{ajohn@lsuc.on.ca}\\

%The Rt. Rev. Mark MacDonald --- \emph{National Indigenous Anglican Bishop}\\
%The Anglican Church of Canada\\
%80 Hayden St.\\
%Toronto, Ontario \textsc{m4y 3g2}\\
%Phone: 416-268-7371\\
%Email: \href{mailto:mmacdonald@national.anglican.ca}{mmacdonald@national.anglican.ca}\\

%The Rev. Canon George Sumner --- \emph{Principal of Wycliffe College, Bishop-elect of the Dioceses of Dallas}\\
%Principal and Helliwell Professor of World Mission\\
%Wycliffe College, 5 Hoskin Ave\\
%Toronto, Ontario \textsc{m5s 1h7}\\
%Phone: 416-946-3521\\
%Email: \href{mailto:george.sumner@wycliffe.utoronto.ca}{george.sumner@wycliffe.utoronto.ca}\\


% INLINE FORMAT FOR REFERENCES

%\parbox{.3\textwidth}{\raggedright
%  Walter Moberly, Professor of Old Testament, Durham\\
%  \href{mailto:r.w.l.moberly@durham.ac.uk}{r.w.l.moberly@durham.ac.uk}}
%\hfill
%\parbox{.3\textwidth}{\raggedright
%  Christopher Seitz, Senior Research Professor, Toronto\\
%  \href{mailto:CSeitz@wycliffe.utoronto.ca}{CSeitz@wycliffe.utoronto.ca}}
%\hfill
%\parbox{.3\textwidth}{\centering
%  Nathan MacDonald, Lecturer in Hebrew Bible, Cambridge\\
%  \href{mailto:nm10011@cam.ac.uk}{nm10011@cam.ac.uk}}
%\hfill
%\parbox{.3\textwidth}{\raggedleft
%  Ephraim Radner, Professor of Historical Theology, Toronto\\
%  \href{mailto:e.radner@wycliffe.utoronto.ca}{e.radner@wycliffe.utoronto.ca}}

% \vspace{1em}
\vfill{}
\hrulefill

\begin{center}
\footnotesize  Updated: \today\\
%\href{http://danieldriver.com/about/}{danieldriver.com/about}
\end{center}

\end{document}
